Viscous Erosion in Porous Media

### 2018-02-27 docs/methods/erosion_methods.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
\caption{2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function $\psi(r,\theta)$ for $\theta \in [-\theta_0, \theta_0]$}.
\label{corner}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.4 \textwidth]{./figs/corner.pdf}
\caption{Schematic of 2D Stokes flow near a corner: The flow around an infinite wedge of opening angle $\oangle$ is described by a stream-function $\psi(r,\theta)$ for $\theta \in [-\theta_0, \theta_0]$}.
\label{corner}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
